---
title: 'UNSCEAR SPCaRT - Metaanalysis - Linda Walsh'
subtitle: 'All Sites'
author: 'Daniel Wollschläger'
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document: 
    number_sections: yes
    keep_tex: no
    fig_crop: no

header-includes:
    \usepackage{pdflscape}
    \newcommand{\blandscape}{\begin{landscape}}
    \newcommand{\elandscape}{\end{landscape}}
---
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      tidy=FALSE,
                      message=FALSE,
                      warning=FALSE,
                      comment=NA,
                      crop=FALSE,
                      fig_crop=FALSE)

options(replace.assign=TRUE,
        width=75,
        digits=4,
        useFancyQuotes=FALSE,
        show.signif.stars=FALSE,
        scipen=999)

output <- knitr::opts_knit$get("rmarkdown.pandoc.to")
```

```{r echo=FALSE}
## Template for studies with overlapping data
## exclude in primary analysis due to overlapping data
## age at exposure < 18
## age at exposure > 18
## EAR/Gy available
## chemo: patients without chemo
## chemo: patients with chemo, adjusted for
## chemo: patients with chemo, not adjusted for
## includes internal exposure? (brachytherapy)

## sensitivity: no external (IRR, SIR etc.)
#####---------------------------------------------------------------------------
#####---------------------------------------------------------------------------
## load packages
## read data
#####---------------------------------------------------------------------------
#####---------------------------------------------------------------------------

library(dplyr)
library(ggplot2)

source("metaanalysis_global.R")
```

```{r eval=FALSE}
library(readxl)

#####---------------------------------------------------------------------------
## run this chunk by hand for reading in data
#####---------------------------------------------------------------------------

#####---------------------------------------------------------------------------
## read in data for different cancer sites
excel_file   <- "SPCaRT_Chapter5_Epidemiology_incomplete first draft_TABLES_08.07.2022.xlsx"
excel_sheets <- list(HaemLym="Tab_5_B_2_Haem_Lymph_meta",
                     Sarcoma="Tab_5_B_3_Sarcoma_meta",
                     Breast ="Tab_5_B_4_Breast_meta",
                     Lung   ="Tab_5_B_5_Lung_meta",
                     Gastro ="Tab_5_B_6_Gastro_meta",
                     Thyroid="Tab_5_B_7_Thyroid_meta",
                     Brain  ="Tab_5_B_8_Brain_meta")

d_RR0_allL <- Map(function(s) { read_xlsx(excel_file, sheet=s) }, excel_sheets)

#####---------------------------------------------------------------------------
## remove studies with overlapping data
overlappingL <- list(HaemLym=c(),
                     Sarcoma=c(),
                     Breast =c("{Inskip, 2009, 19620485}",      # overlap Veiga 2019
                               "{Schonfeld, 2020, 31794291}",   # overlap Veiga 2019
                               "{van Leeuwen, 2003, 12837833}", # overlap Travis 2003
                               "{Rubino, 2003, 12942115}"),     # overlap Guibout 2005
                     Lung   =c(),
                     Gastro =c(),
                     Thyroid=c(),
                     Brain  =c())

d_RR0_selL <- Map(function(x, y) { x %>% filter(!(Reference %in% y)) },
                  d_RR0_allL, overlappingL)

#####---------------------------------------------------------------------------
## fill in missing information such as CI boundaries, reference doses
## thyroid: downturn in dose-response at high doses -> set threshold
dose_thresh_thyroid <- 10

d_RR_allL <- Map(rr_impute_missing, d_RR0_allL)
d_RR_selL <- Map(rr_impute_missing, d_RR0_selL)

d_RR_allL$Thyroid <- d_RR_allL$Thyroid %>%
    filter(is.na(d_kPrime) | (d_kPrime < dose_thresh_thyroid))

d_RR_selL$Thyroid <- d_RR_selL$Thyroid %>%
    filter(is.na(d_kPrime) | (d_kPrime < dose_thresh_thyroid))

#####---------------------------------------------------------------------------
## save to file
saveRDS(d_RR0_allL, file="d_RR0_allL.rda")
saveRDS(d_RR0_selL, file="d_RR0_selL.rda")
saveRDS(d_RR_allL,  file="d_RR_allL.rda")
saveRDS(d_RR_selL,  file="d_RR_selL.rda")
```

```{r eval=FALSE}
#####---------------------------------------------------------------------------
## run this chunk by hand to re-do estimating ERR/Gy + CI from category RRs
#####---------------------------------------------------------------------------

n_repl <- 1000

d_RR0_allL <- readRDS("d_RR0_allL.rda")
d_RR0_selL <- readRDS("d_RR0_selL.rda")
d_RR_allL  <- readRDS("d_RR_allL.rda")
d_RR_selL  <- readRDS("d_RR_selL.rda")

d_ERR_allL <- Map(get_all_ERR_from_RR, d_RR_allL, n_repl=n_repl)
## TODO: unnecessary duplication
d_ERR_selL <- Map(get_all_ERR_from_RR, d_RR_selL, n_repl=n_repl)

saveRDS(d_ERR_allL, file="d_ERR_allL.rda")
saveRDS(d_ERR_selL, file="d_ERR_selL.rda")

#####---------------------------------------------------------------------------
## sensitivity: different dose thresholds for thyroid
#####---------------------------------------------------------------------------

## 5 Gy
dose_thresh_thyroid <- 5
d_RR_sel <- rr_impute_missing(d_RR0_selL$Thyroid) %>%
    filter(is.na(d_kPrime) | (d_kPrime < dose_thresh_thyroid))

d_ERR_selL <- get_all_ERR_from_RR(d_RR_sel, n_repl=n_repl)
saveRDS(d_ERR_selL$d_ERR_wide,
        file=paste0("d_ERR_thyroid_thresh",
                    sprintf("%.2d", dose_thresh_thyroid), "_sel_wide.rda"))

## 20 Gy
dose_thresh_thyroid <- 20
d_RR_sel <- rr_impute_missing(d_RR0_selL$Thyroid) %>%
    filter(is.na(d_kPrime) | (d_kPrime < dose_thresh_thyroid))

d_ERR_selL <- get_all_ERR_from_RR(d_RR_sel, n_repl=n_repl)
saveRDS(d_ERR_selL$d_ERR_wide,
        file=paste0("d_ERR_thyroid_thresh",
                    sprintf("%.2d", dose_thresh_thyroid), "_sel_wide.rda"))
```

```{r}
#####---------------------------------------------------------------------------
## load previously generated data and estimates
#####---------------------------------------------------------------------------

d_RR_allL  <- readRDS("d_RR_allL.rda")
d_RR_selL  <- readRDS("d_RR_selL.rda")
d_ERR_allL <- readRDS("d_ERR_allL.rda")
d_ERR_selL <- readRDS("d_ERR_selL.rda")

#####---------------------------------------------------------------------------
#####---------------------------------------------------------------------------
```

**CAVE** "RR" here may refer to RR, OR, HR

# Methods
## ERR/Gy from category-specific RRs + CIs

  * Approach as in: Doi et al. 2014: https://doi.org/10.1093/jrr/rru045
  * However, modified step of estimating ERR/Gy based on category-specific RRs.
      * Instead of weighted linear regression with least squares following Little 2001: (https://doi.org/10.1080/09553000010022634) use weighted generalized least squares regression to take into account correlated category RRs, assuming homogeneous correlation matrix with off-diagonal 0.5 per study (based on quick simulation study) following Berrington and Cox. 2003. https://doi.org/10.1093/biostatistics/4.3.423

## Metaanalysis

  * ERRs as given in the publication (if available) or as estimated from category RRs (preferred: gls approach, uncorrelated approach if gls does not converge)
  * SE of log(ERR) derived from CI width assuming log-normality
  * Metaanalysis uses log(ERR+1) as input together with SE on log scale for weighting
  * Metaanalysis results are back-transformed using exp(logRR) - 1

## Sensitivity: Synthetic single ERR estimate from all studies with category RRs

  * Use all per-study category RRs in a single generalized least squares regression model
  * Within-study RRs: assume homogeneous correlation matrix with off-diagonal 0.5
  * Assume no correlation between study RRs
  * Random effects metaanalysis using synthetic single estimate from category-RR-only studies and studies with ERR/Gy

# Haematopoetic / Lymph

```{r}
cancer_site <- "HaemLym"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 30)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 30)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position="bottom")
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-0.5, 13)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

# Sarcoma

```{r}
cancer_site <- "Sarcoma"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 80)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 80)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position=c(0.85, 0.12))
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-1.2, 23)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

# Breast

```{r}
cancer_site <- "Breast"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel,
       aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
           color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 10)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

Note: For Veiga 2019, ERR derived from OR/10 Gy is plotted.

```{r fig.height=8}
d_ERR_Veiga <- d_RR_sel %>%
    filter(auth_year == "Veiga_2019") %>%
    mutate(ERR     =RR-1,
           ERR_CIlo=RR_CIlo-1,
           ERR_CIup=RR_CIup-1,
           from="org") %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    slice(1)

d_ERR_sub <- d_ERR_long %>%
    filter(!((auth_year == "Veiga_2019") & (from == "org")))

d_ERR_plot <- bind_rows(d_ERR_sub, d_ERR_Veiga)

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=bind_rows(d_ERR_sub, d_ERR_Veiga),
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 15)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position=c(0.85, 0.12))
```

Only Svahn-Tapper 2006 (off the charts)

```{r}
d_ERR_ribbon_ST2006 <- d_ERR_ribbon %>%
    filter(auth_year == "Svhn-Tp_2006")

d_ERR_long_ST2006 <- d_ERR_long %>%
    filter(auth_year == "Svhn-Tp_2006")

d_RR_ST2006 <- d_RR_sel %>%
    filter(auth_year == "Svhn-Tp_2006")

ggplot(d_RR_ST2006) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon_ST2006,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_long_ST2006,
                aes(intercept=1, slope=ERR, color=from)) +
    geom_abline(data=d_RR_ST2006,
                aes(intercept=0, slope=RR)) +
    coord_cartesian(ylim=c(0, 100)) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    facet_grid(~ auth_year) +
    ggpt +
    theme(legend.position="bottom")
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-1, 4.5)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

# Lung

```{r}
cancer_site <- "Lung"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 20)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 15)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position="bottom")
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-0.2, 2.5)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

# Gastro

```{r}
cancer_site <- "Gastro"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 10)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 15)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position="bottom")
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-0.2, 2.5)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

# Thyroid

```{r}
cancer_site <- "Thyroid"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis - dose threshold 10 Gy
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 10)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 15)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position=c(0.85, 0.12))
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-1.2, 20)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

## Dose threshold 5 Gy

```{r}
dose_thresh <- 5
d_ERR_wide <- readRDS(paste0("d_ERR_thyroid_thresh",
                             sprintf("%.2d", dose_thresh), "_sel_wide.rda"))

d_ERR_wide_ma <- d_ERR_wide %>%
    mutate(## take original ERR+CI if available, else use estimated ERR+CI
           used       =get_used(ERR_org,         ERR_gls,         ERR_lm),
           ERR        =coalesce(ERR_org,         ERR_gls,         ERR_lm),
           ERR_CIlo   =coalesce(ERR_CIlo_org,    ERR_CIlo_gls,    ERR_CIlo_lm),
           ERR_CIup   =coalesce(ERR_CIup_org,    ERR_CIup_gls,    ERR_CIup_lm),
           ERR_SE_meta=coalesce(ERR_SE_meta_org, ERR_SE_meta_gls, ERR_SE_meta_lm))
```

```{r, child='metaanalysis_child_meta.Rmd'}
```

## Dose threshold 20 Gy

```{r}
dose_thresh <- 20
d_ERR_wide <- readRDS(paste0("d_ERR_thyroid_thresh",
                             sprintf("%.2d", dose_thresh), "_sel_wide.rda"))

d_ERR_wide_ma <- d_ERR_wide %>%
    mutate(## take original ERR+CI if available, else use estimated ERR+CI
           used       =get_used(ERR_org,         ERR_gls,         ERR_lm),
           ERR        =coalesce(ERR_org,         ERR_gls,         ERR_lm),
           ERR_CIlo   =coalesce(ERR_CIlo_org,    ERR_CIlo_gls,    ERR_CIlo_lm),
           ERR_CIup   =coalesce(ERR_CIup_org,    ERR_CIup_gls,    ERR_CIup_lm),
           ERR_SE_meta=coalesce(ERR_SE_meta_org, ERR_SE_meta_gls, ERR_SE_meta_lm))
```

```{r, child='metaanalysis_child_meta.Rmd'}
```

# Brain

```{r}
cancer_site <- "Brain"

d_RR_all     <- d_RR_allL[[cancer_site]]
d_RR_sel     <- d_RR_selL[[cancer_site]]
d_ERR_all_lw <- d_ERR_allL[[cancer_site]]
d_ERR_sel_lw <- d_ERR_selL[[cancer_site]]
d_ERR_long   <- d_ERR_sel_lw$d_ERR_long
d_ERR_wide   <- d_ERR_sel_lw$d_ERR_wide
```

## Primary analysis
### Category RR + CIs

```{r fig.height=6}
ggplot(d_RR_sel, aes(x=d_kPrime, y=RR_cat, ymin=RR_cat_CIlo, ymax=RR_cat_CIup,
                  color=auth_year)) +
    geom_point() +
    geom_linerange() +
    coord_cartesian(ylim=c(0, 60)) +
    xlab("Dose [Gy]") +
    ylab("RR category") +
    ggpt +
    theme(legend.position="bottom",
          legend.title=element_blank())
```

### Estimated per-study ERR + CIs with category RR + CIs

```{r fig.height=8}
# d_ERR_Finke <- d_RR_sel %>%
#     filter(auth_year == "Finke_2015") %>%
#     mutate(ERR     =RR-1,
#            ERR_CIlo=RR_CIlo-1,
#            ERR_CIup=RR_CIup-1,
#            from="org") %>%
#     select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
#     slice(1)
# 
# d_ERR_sub <- d_ERR_long %>%
#     filter(!((auth_year == "Finke_2015") & (from == "org")))
# 
# d_ERR_plot <- bind_rows(d_ERR_sub, d_ERR_Finke)
d_ERR_plot <- d_ERR_long

d_ribbon <- data.frame(d_kPrime=seq(from=min(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    to  =max(d_RR_sel$d_kPrime, na.rm=TRUE),
                                    length.out=2))

d_ERR_ribbon <- d_ERR_plot %>%
    full_join(d_ribbon, by=character()) %>%
    mutate(ERR_CI_Ylo=1 + d_kPrime*ERR_CIlo,
           ERR_CI_Yup=1 + d_kPrime*ERR_CIup)

ggplot(d_RR_sel) +
    geom_point(aes(x=d_kPrime, y=RR_cat)) +
    geom_linerange(aes(x=d_kPrime, y=RR_cat,
                       ymin=RR_cat_CIlo, ymax=RR_cat_CIup)) +
    geom_ribbon(data=d_ERR_ribbon,
                aes(x=d_kPrime, ymin=ERR_CI_Ylo, ymax=ERR_CI_Yup,
                    color=from, fill=from), alpha=0.3, linetype=0) +
    geom_abline(data=d_ERR_plot,
                aes(intercept=1, slope=ERR, color=from)) +
    coord_cartesian(ylim=c(0, 60)) +
    facet_wrap(~ auth_year) +
    xlab("Dose [Gy]") +
    ylab("RR") +
    ggpt +
    theme(legend.position=c(0.85, 0.12))
```

### Estimated ERR + CIs with original ERR + CIs

```{r results="asis"}
d_ERR_long %>%
    select(auth_year, from, ERR, ERR_CIlo, ERR_CIup) %>%
    knitr::kable(booktabs=TRUE)
```

```{r fig.height=6}
ggplot(d_ERR_plot,
       aes(x=auth_year, y=ERR,
           group=from,
           color=from,
           shape=from,
           ymin=ERR_CIlo,
           ymax=ERR_CIup)) +
    geom_point(position=position_dodge(width=0.75)) +
    geom_linerange(position=position_dodge(width=0.75)) +
    xlab(NULL) +
    coord_flip(ylim=c(-0.1, 15)) +
    ggpt +
    theme(legend.position=c(0.9, 0.2))
```

### Metaanalysis

```{r, child='metaanalysis_child_primary_meta.Rmd'}
```

## Sensitivity Analyses

```{r, child='metaanalysis_child_sensitivity.Rmd'}
```

\blandscape

# All solid cancer
## Primary analysis
### Metaanalysis

```{r}
cancer_sites_solid <- c("Sarcoma",
                        "Breast",
                        "Lung",
                        "Gastro",
                        "Thyroid",
                        "Brain")

tables_err_solid <- paste0("d_ERR_site_", cancer_sites_solid)

d_ERR_wide_ma <- do.call("bind_rows", lapply(tables_err_solid, try_get)) %>%
    filter(used != "none") %>%
    select(-weight) %>%
    rename(ERR_SE_meta=ERR_SE)

cancer_site <- "all_solid"
meta_type   <- "special"
```

```{r, child='metaanalysis_child_meta.Rmd'}
```

# Combined results
## ERRs used as input for metaanalysis

```{r, results="asis"}
cancer_sites <- c("HaemLym",
                  "Sarcoma",
                  "Breast",
                  "Lung",
                  "Gastro",
                  "Thyroid",
                  "Brain")

sens_types <- c("primary",
                "sens_uncorr",
                "sens_synth1",
                "sens_withoverlap",
                "sens_onlyorg",
                "sens_orgscale")
```

```{r}
tables_err_site <- paste0("d_ERR_site_", cancer_sites)

tables_err_all <- do.call("bind_rows", lapply(tables_err_site, try_get)) %>%
    filter(used != "none") %>%
    select(site, auth_year, everything())

writexl::write_xlsx(tables_err_all, "table_err_all.xlsx")

tables_err_all %>%
    knitr::kable()
```

## Metaanalysis results (primary)

```{r}
d_tables_meta_site <- expand.grid(cs=cancer_sites, st=sens_types)
tables_meta_site   <- paste0("d_meta_",
                             d_tables_meta_site$cs, "_",
                             d_tables_meta_site$st)

tables_meta_all <- do.call("bind_rows", lapply(tables_meta_site, try_get)) %>%
    mutate(site=factor(site, levels=cancer_sites),
           type=factor(type, levels=rev(sens_types))) %>%
    select(site, everything())

tables_meta_all %>%
    filter(type == "primary") %>%
    select(-type) %>%
    knitr::kable()
```

\elandscape

## Metaanalysis results (primary and sensitivity)

```{r fig.height=8}
ggplot(tables_meta_all,
       aes(x=type, y=ERR, ymin=ERR_CIlo, ymax=ERR_CIup, color=type)) +
    geom_point(position=position_dodge(width=0.3)) +
    geom_linerange(position=position_dodge(width=0.3)) +
    geom_hline(yintercept=0, col="darkgray") +
    xlab("Metaanalysis type") +
    ylab(expression(paste('ERR ', Gy^-1, ' with 95% CI'))) +
    # scale_y_log10() +
    coord_flip() +
    facet_grid(site ~ .) +
    ggpt +
    theme(legend.position="none")
```

Without sarcoma, thyroid and brain due to different magnitude

```{r fig.height=5}
ggplot(tables_meta_all %>% filter(!(site %in% c("Sarcoma", "Thyroid", "Brain"))),
       aes(x=type, y=ERR, ymin=ERR_CIlo, ymax=ERR_CIup, color=type)) +
    geom_point(position=position_dodge(width=0.3)) +
    geom_linerange(position=position_dodge(width=0.3)) +
    geom_hline(yintercept=0, col="darkgray") +
    xlab("Metaanalysis type") +
    ylab(expression(paste('ERR ', Gy^-1, ' with 95% CI'))) +
    # scale_y_log10() +
    coord_flip() +
    facet_grid(site ~ .) +
    ggpt +
    theme(legend.position="none")
```
